% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Junjie Qiu}

\basicInfo{
  \email{qiujj@mail.sustech.edu.cn} \textperiodcentered\ 
  \phone{(+86) 15198598764} \textperiodcentered\ 
  \linkedin[Junjie Qiu]{https://www.linkedin.com/in/junjie-qiu-35117a2bb/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Southern University of Science and Technology (SUSTech)}, Shenzhen, China}{2021 -- Present}
\textit{Undergraduate student} in Data Science and Big Data Technology, expected June 2025
\begin{itemize}
    \item GPA: 3.89/4.0 | Ranking: 4/50 | Supervised by Prof. Doc. Yifang Ma, STATDS, SUSTech
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Center for Computational Science and Engineering.} SUSTech}{Mar. 2024 -- Present}
\role{Student Assistant Engineer}{Supervised by Dr. Jing Fan, CCSE, SUSTech}
Brief introduction: Assist engineers to install and test clusters, help center users solve hardware and software problems, and participate in high-performance application development.
\begin{itemize}
  \item Installed a blade node and solved a network adapter error
  \item Blog: \href{TODO}{TODO}
\end{itemize}

\datedsubsection{\textbf{ASC24 Student Supercompting Challenge.} Shanghai, China}{Nov. 2023 -- April. 2024}
\role{Major in AI challenge}{\textit{\nth{1} Prize \& Final List}. Ranked \textit{\nth{10} place} in the preliminary stage.}
Brief introduction: In the competition, students were asked to build their own cluster on site and optimize the hardware and software for multiple competition questions under constraints such as 3kw power consumption. During the preliminary and final rounds, he was responsible for the AI challenge. 
\begin{itemize}
  \item Optimized LLM inference speed by 800\% under constraints in the preliminary stage
  \item Blog: \href{TODO}{TODO}
\end{itemize}

\datedsubsection{\textbf{2023 CUMCM Mathematical Contest in Modeling}}{Sep. 2023}
\role{Team Member}{\textit{\nth{2} Prize}, Guangdong}
\begin{itemize}
    \item Blog: \href{TODO}{TODO}
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python > C++ > Java > SAS > R
  \item Platform: Linux
  \item Development: Pytorch, Spark, SQL, OpenMP, CUDA, Docker
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{2} Prize}, Award on Merit Student Scholarship for Exceptional Performance, SUSTech}{Sep. 2022}
\datedline{\textit{\nth{3} Prize}, Award on Merit Student Scholarship for Exceptional Performance, SUSTech}{Sep. 2023}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item TOEFL iBT:
  \item Blog: \href{https://haroqiu.zeabur.app/}{https://haroqiu.zeabur.app/}
  \item GitHub: \href{https://github.com/Harold-QIU}{https://github.com/Harold-QIU}
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
